Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-19 paper/icml_drau/relatedworks.tex

Our approach builds on \cite{adv_upd}, who identified the collapse of
$Q$-learning for small time steps and, as a solution, suggested the Advantage
Updating algorithm, with proper $\deltat$ scalings for the $V$ part and
the advantage part; testing was only done on a quadratic-linear problem.

@@

The problem studied here is a continuity effect quite distinct from
multiscale RL approaches: indeed the issue arises even if there
is only one timescale in the environment. Arguably, a small
$\deltat$ can be seen as a mismatch between the algorithm's
timescale and the physical system's timescale, but the collapse of the
$Q$ function to the $V$ function is an intrinsic mathematical phenomenon from time
continuity, and cannot obviously be addressed via existing multiscale
techniques. \TODO{cite something!}

>>>>

Our approach builds on \cite{adv_upd},  who identified the collapse of
$Q$-learning for small time steps and, as a solution, suggested the Advantage
Updating algorithm, with proper $\deltat$ scalings for the $V$ part and
the advantage part; testing was only done on a quadratic-linear problem.
\TODO{mention that Baird did not experimentally study robustness}

@@

The problem studied here is a continuity effect quite distinct from
multiscale RL approaches: indeed the issue arises even if there
is only one timescale in the environment. Arguably, a small
$\deltat$ can be seen as a mismatch between the algorithm's
timescale and the physical system's timescale, but the collapse of the
$Q$ function to the $V$ function is an intrinsic mathematical phenomenon \TODO{arising} from time
continuity, and cannot obviously be addressed via existing multiscale
techniques. \TODO{cite something!}
